%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
%\renewcommand{\headrulewidth}{0pt}
%\renewcommand{\footrulewidth}{0pt}

% Adjust margins
 % Use the custom resume.cls style

\usepackage[left=0.2 in,top=0.2in,right=0.2 in,bottom=0.2 in]{geometry} %

\urlstyle{same}

\raggedbottom
\raggedright
%\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \ifx&#3&\else\textit{\small #3} & \textit{\small #4} \\\fi
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

%\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-3pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Avichal Baweja} \\ \vspace{1pt}
    \small +91 9837452284 $|$ \href{mailto:avichalbaweja@gmail.com}{\underline{avichalbaweja@gmail.com}} $|$
    \href{https://www.linkedin.com/in/avichalbaweja29/}{\underline{linkedin.com/in/avichalbaweja29}} $|$
    \href{https://github.com/avichal29}{\underline{github.com/Avichal29}}
\end{center}

\section{SUMMARY}
Founding Engineer with expertise in backend development, AI-driven systems, and scalable product architecture. Experienced in building end-to-end platforms in fast-paced startup environments. Proficient in Python, FastAPI, Docker, and cloud deployments with a proven ability to translate business needs into impactful technical solutions.

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Founding Engineer $|$ \textit{Datavedam}}{Oct 2025 -- Present}
      {}{}
      \resumeItemListStart
        \resumeItem{Built and scaled a multi-product AI-driven platform from the ground up, including chatbot systems, automation tools, and data-driven applications.}
        \resumeItem{Designed scalable backend services using Python (FastAPI) and integrated APIs for automation, analytics, and communication workflows.}
        \resumeItem{Architected multi-tenant systems supporting customization across projects; built data pipelines enabling real-time querying and decision-making.}
        \resumeItem{Managed DevOps workflows using Docker and cloud infrastructure, ensuring smooth CI/CD and production reliability.}
        \resumeItem{Optimized system performance and reduced latency for handling concurrent users and real-time requests.}
      \resumeItemListEnd

    \resumeSubheading
      {Business Analyst $|$ \textit{Purshotam Profiles Pvt. Ltd.}}{Jan 2025 -- July 2025}
      {}{}
      \resumeItemListStart
        \resumeItem{Identified new business opportunities in solar projects sector; prepared proposals and performance reports for client engagement.}
        \resumeItem{Collaborated with cross-functional teams to optimize sales processes and improve operational efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Vision Intern $|$ \textit{TechEagle Innovations Pvt. Ltd.}}{Apr 2024 -- May 2024}
      {}{}
      \resumeItemListStart
        \resumeItem{Developed a CV-based drone system integrating YOLOv5 with real-time feedback control for autonomous navigation and obstacle avoidance.}
        \resumeItem{Designed an autonomous landing system in ROS/Gazebo using Python, OpenCV, and ArUco markers for precise landings.}
      \resumeItemListEnd

    \resumeSubheading
      {IT Intern $|$ \textit{Sankalptaru Foundation}}{Jan 2023 -- Mar 2023}
      {}{}
      \resumeItemListStart
        \resumeItem{Built predictive models (Python, Pandas, scikit-learn) forecasting farm conditions; performed demand analysis with Matplotlib.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.2in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks:} Python, FastAPI, SQL, React, REST APIs \\
     \textbf{AI/ML \& Data:} Machine Learning, Computer Vision, OCR, RAG Systems, LLMs \\
     \textbf{Tools \& Infrastructure:} Docker, Git, CI/CD, Cloud Deployment
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Event Planner} $|$ \emph{React, FastAPI, REST API}}{}
          \resumeItemListStart
            \resumeItem{Built a full-stack event management platform with an integrated LLM-powered AI assistant for automated event descriptions and RSVP handling.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Handwritten Text to LaTeX Converter} $|$ \emph{Python, OCR, Image Processing, ML}}{}
          \resumeItemListStart
            \resumeItem{Built an OCR + LLM pipeline to extract handwritten notes and generate accurate LaTeX documents, with optimized prompts for math expressions.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Trackpad Control using Hand Gestures} $|$ \emph{Python, OpenCV, MediaPipe, PyAutoGUI}}{}
          \resumeItemListStart
            \resumeItem{Developed a real-time hand gesture-based trackpad control system with efficient tracking and high-accuracy gesture detection.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Christ University}{Bengaluru, Karnataka}
      {B.Tech. Computer Science \& Engineering, Honors in AI \& ML}{2021 -- 2025}
    \resumeSubheading
      {Delhi Public School}{Agra, Uttar Pradesh}
      {Senior Secondary School}{2019 -- 2021}
  \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}