%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
 % Use the custom resume.cls style

\usepackage[left=0.2 in,top=0.2in,right=0.2 in,bottom=0.2 in]{geometry} % 

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,topmargin=0.10in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-10pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Avichal Baweja} \\ \vspace{1pt}
    \small +91 9837452284 $|$ \href{mailto:avichalbaweja@gmail.com}{\underline{avichalbaweja@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/avichalbaweja29/}{\underline{linkedin.com/in/avichalbaweja29}} $|$
    \href{https://github.com/avichal29}{\underline{github.com/Avichal29}}
\end{center}
\section{SUMMARY}
Results-driven and detail-oriented professional with a strong background in client relationship management, market research, and business growth strategies. Experienced in identifying new business opportunities, developing partnerships, and supporting sales initiatives to drive revenue growth. Skilled in preparing presentations, creating reports, and optimizing workflows to enhance efficiency, strengthen client engagement, and support data-driven decision-making.
%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Christ University}{Bengaluru, Karnataka}
      {B.Tech. Computer Science \& Engineering, Honors in AI \& ML}{2021 -- 2025}
    \resumeSubheading
      {Delhi Public School}{Agra, Uttar Pradesh}
      {High School \& Senior Secondary School }{2007 -- 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Business Development Associate $|$ $Purshotam$ $Profiles$ $Pvt.$ $Ltd.$ }{Jan 2025 -- Present}
      {}{}
      \resumeItemListStart
        \resumeItem{Researched and identified new business opportunities in the solar projects sector to support revenue growth.}
        \resumeItemListEnd
        \resumeItemListStart
        \resumeItem {Prepared presentations, proposals, and performance reports to strengthen client engagement and decision-making.}
        \resumeItemListEnd
        \resumeItemListStart
        \resumeItem{Collaborated with cross-functional teams to optimize sales processes and improve operational efficiency.}
        \resumeItemListEnd
    \resumeSubheading
      {Computer Vision Intern$|$ $TechEagle$ $Innovations$ $Pvt.$ $Ltd.$ (2 Months) }{April 2024 -- May 2024}
      {}{}
      \resumeItemListStart
        \resumeItem{Developed a computer vision–based drone system by integrating YOLOv5 with real-time feedback control for stability, autonomous navigation, and obstacle avoidance.}
    \resumeItemListEnd
    \resumeItemListStart
        \resumeItem{Designed and simulated an autonomous landing system in ROS and Gazebo using Python, OpenCV, and ArUco markers for precise coordinate-based landings.}
    \resumeItemListEnd
    
    \resumeSubheading
      {IT Intern $|$ $Sankalptaru$ $Foundation$}{Jan. 2023 -- March 2023}
      {}{}
   
      \resumeItemListStart
        \resumeItem{Built predictive models (Python, Pandas, scikit-learn) forecasting farm conditions to boost agroforestry planning.}
    \resumeItemListEnd
    \resumeItemListStart
        \resumeItem{Performed demand analysis with Matplotlib and statistics to support sustainable farming strategy.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin= 0.2in, label={}]
    \small{\item{
     \textbf{Python, C, Excel,  Java(basics), PowerBi, Tableau, Machine Learning, React, FastAPI} \\}}
 \end{itemize}
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Event Planner} $|$ {React, FastAPI, Rest API}}{}
          \resumeItemListStart
            \resumeItem{Built a web-based platform using React (frontend) and FastAPI (backend) with integrated AI assistant for automated event description generation.}
          \resumeItemListEnd
          \resumeItemListStart
            \resumeItem{Implemented LLM-powered prompts to streamline event management, including RSVP handling and personalized content creation.}
          \resumeItemListEnd
          
    

    \resumeProjectHeading
          {\textbf{Converting of Handwritten text to Latex} $|$ \emph{Python, OCR, Image Processing, ML}}{}
          \resumeItemListStart
            \resumeItem{ Built a pipeline using OCR to extract text from handwritten notes and LLM-based prompt templates to generate accurate LaTeX documents.}
         \resumeItemListEnd
         \resumeItemListStart
            \resumeItem{Automated conversion process to improve efficiency and reduce manual formatting effort in academic and research workflows.}
         \resumeItemListEnd
         \resumeItemListStart
            \resumeItem{Optimized output quality by fine-tuning prompts for mathematical expressions and structured formatting.}
         \resumeItemListEnd
         
    \resumeProjectHeading
          {\textbf{Trackpad Control using Hand Gestures} $|$ \emph{Python, OpenCV, MediaPipe, PyAutoGUI, NumPy}}{}
          \resumeItemListStart
            \resumeItem{Developed a real-time hand gesture–based trackpad control system with efficient hand tracking and smooth user interaction.}
         \resumeItemListEnd
         \resumeItemListStart
            \resumeItem{Optimized the processing pipeline to ensure high responsiveness and accuracy in gesture detection.}
         \resumeItemListEnd
    \resumeSubHeadingListEnd
%







%-------------------------------------------
\end{document}
