%-------------------------
% AI Product Engineer Resume - ATS Optimized
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0pt}
%\renewcommand{\footrulewidth}{0pt}

\usepackage[left=0.20 in,top=0.18in,right=0.20 in,bottom=0.18 in]{geometry}

\urlstyle{same}
\raggedbottom
\raggedright
%\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

\pdfgentounicode=1

\setlist[itemize]{itemsep=0pt,topsep=2pt,parsep=0pt,partopsep=0pt}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-1pt}
}

%\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-3pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Avichal Baweja} \\ \vspace{1pt}
    \small +91 9837452284 $|$ \href{mailto:avichalbaweja@gmail.com}{\underline{avichalbaweja@gmail.com}} $|$
    \href{https://www.linkedin.com/in/avichalbaweja29/}{\underline{linkedin.com/in/avichalbaweja29}} $|$
    \href{https://github.com/avichal29}{\underline{github.com/Avichal29}}
\end{center}

\section{SUMMARY}
AI Product Engineer with strong expertise in building and deploying AI-powered products from concept to production. Proven expertise in translating user requirements into technical solutions, developing AI features, and product strategy. Experienced in fast-paced startup environments with end-to-end ownership of product development.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.2in, label={}]
    \small{\item{
    \textbf{AI Product Development:} Product Strategy, User Research, MVP Development, A/B Testing, AI Agents \\
    \textbf{AI/ML Integration:} RAG Systems, Computer Vision, OCR/OMR, LLM Integration, Chatbots \\
    \textbf{Frontend Development:} React, TypeScript, UX Design, Responsive Design \\
    \textbf{Backend Systems:} API Design, Microservices, Database Architecture, Cloud Deployment, FastAPI \\
    }}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Founding Engineer}{Oct 2025 -- Present}
      {Datavedam}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Designed and developed AI agent-based School ERP platform from concept to production.}
        \resumeItem{Built RAG pipeline that scrapes CBSE circulars and converts them into vector embeddings for intelligent querying.}
        \resumeItem{Built OCR/OMR pipelines for document and exam processing with automated workflows.}
        \resumeItem{Contributed to product strategy, feature prioritization, and system design beyond traditional engineering.}
        \resumeItem{Collaborated closely with stakeholders to translate business requirements into technical solutions.}
      \resumeItemListEnd
    \resumeSubheading
      {Business Analyst}{Jan 2025 -- July 2025}
      {Purshotam Profiles Pvt. Ltd.}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Identified new business opportunities in solar projects sector; prepared proposals and performance reports for client engagement.}
        \resumeItem{Collaborated with cross-functional teams to optimize sales processes and improve operational efficiency.}
      \resumeItemListEnd
    \resumeSubheading
      {Computer Vision Intern}{April 2024 -- May 2024}
      {TechEagle Innovations Pvt. Ltd.}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a CV-based drone system integrating YOLOv5 with real-time feedback control for autonomous navigation and obstacle avoidance.}
        \resumeItem{Designed an autonomous landing system in ROS/Gazebo using Python, OpenCV, and ArUco markers for precise landings.}
      \resumeItemListEnd
    \resumeSubheading
      {IT Intern}{Jan 2023 -- March 2023}
      {Sankalptaru Foundation}{Remote}
      \resumeItemListStart
        \resumeItem{Built predictive models (Python, Pandas, scikit-learn) forecasting farm conditions; performed demand analysis with Matplotlib.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Datavedam - AI Powered School ERP Platform}}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Implemented AI agents (Welfare Agent, AI Copilot) for automated admin and operational tasks.}
        \resumeItem{Built QR-code admission workflow; integrated multiple APIs for end-to-end school automation.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Drone Computer Vision System (TechEagle)}}{April 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{Integrated YOLOv5 with real-time feedback control; designed autonomous landing using OpenCV and ArUco markers.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Manufacturing Dispatch Management Portal}}{}
      \resumeItemListStart
        \resumeItem{Designed centralized web portal for 15+ manufacturing plants; automated dispatch workflows and GRN reconciliation.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Event Planner}}{}
      \resumeItemListStart
        \resumeItem{Built full-stack platform (React + FastAPI) with LLM-powered AI assistant for automated event descriptions and RSVP handling.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Handwritten Text to LaTeX Converter}}{}
      \resumeItemListStart
        \resumeItem{Built OCR + LLM pipeline to extract handwritten notes and generate accurate LaTeX documents with optimized math prompts.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Christ University}{Bengaluru, Karnataka}
      {B.Tech. Computer Science \& Engineering, Honors in AI \& ML}{2021 -- 2025}
    \resumeSubheading
      {Delhi Public School}{Agra, Uttar Pradesh}
      {Senior Secondary School}{2019 -- 2021}
\resumeSubHeadingListEnd

\end{document}